---
title: "Bird activities in the face of the pressure wave from the volcanic eruption in tonga"
author: "lorrilliere"
date: "24/01/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importation data


```{r ids, include=FALSE}
  id_cor <- 1266784970 
  id_cur <- 1077731101
```


Importation data from two research programs: 
 - Corvus corone [ID_PROG 883], movebank ID : `r id_cor`
 - Eurasian Curlew [ID_PROG 1083], movebank ID : `r id_cur`
 
 We get data directly thank to the move package. 


```{r package, include=FALSE}
  vecPackage=c("move","lubridate","ggplot2","ggmap","sf","ggspatial","data.table")#,"moveVis",suncalc","HelpersMG","adehabitatHR","rtide")
ip <- installed.packages()[,1]

for(p in vecPackage){
    if (!(p %in% ip))
        install.packages(pkgs=p,repos = "https://pbil.univ-lyon1.fr/CRAN/",dependencies=TRUE)
    library(p,character.only = TRUE)

}



```


```{r cars, include=FALSE}
    setwd("C:/git/Migration/eruption")
    pw <- readLines("library/pw.txt")
    username <-"romainlorrilliere"
    log <- movebankLogin(username,pw)
 
    d_cor <- as.data.frame(getMovebankData(study=id_cor,login=log,removeDuplicatedTimestamps=TRUE,timestamp_start="20220115000000000",timestamp_end="20220116000000000"))
    
  setDT(d_cor)
    d_cor[,name := substr(local_identifier,1,4)]
    d_cor[,species := "crow"]
    
    
    
    
    d_cur <- as.data.frame(getMovebankData(study=id_cur,login=log,removeDuplicatedTimestamps=TRUE,timestamp_start="20220115000000000",timestamp_end="20220116000000000"))
    
  setDT(d_cur)
  local_identifier <- unique(d_cur[,local_identifier])
  #  t_name <- data.frame(local_identifier,name = local_identifier)
  #fwrite(t_name,"library/name_curlew.csv")
  t_name <- fread("library/name_curlew.csv")
  d_cur <- merge(d_cur,t_name,by="local_identifier",all.x=TRUE)
   setDT(d_cur)
    d_cur[,species := "curlew"]
    

    lescol <- c("species","taxon_canonical_name","name","local_identifier","tag_id","sensor_type_id","acceleration_raw_x","acceleration_raw_y","acceleration_raw_z","barometric_height","external_temperature","ground_speed","heading","height_above_msl","light_level","location_lat","location_long","magnetic_field_raw_x","magnetic_field_raw_y","magnetic_field_raw_z","timestamp","update_ts","deployment_id","event_id","individual_id")
    
    d_cor <- d_cor[,lescol,with=FALSE]
    d_cur <- d_cur[,lescol,with=FALSE]
    
    d <- rbind(d_cor,d_cur)
    setDT(d)
    
    
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}


gg <- ggplot(data  = d, aes(x = timestamp,y = acceleration_raw_x, colour=name,group=name))+ facet_grid(species~.)
gg <- gg + geom_line()
gg

gg <- ggplot(data  = d, aes(x = timestamp,y = acceleration_raw_y, colour=name,group=name))+ facet_grid(species~.)
gg <- gg + geom_line()
gg

gg <- ggplot(data  = d, aes(x = timestamp,y = acceleration_raw_z, colour=name,group=name))+ facet_grid(species~.)
gg <- gg + geom_line()
gg


gg <- ggplot(data  = d, aes(x = timestamp,y = heading, colour=name,group=name))+ facet_grid(species~.)
gg <- gg + geom_line()
gg


gg <- ggplot(data  = d, aes(x = timestamp,y = ground_speed, colour=name,group=name))+ facet_grid(species~.)
gg <- gg + geom_line()
gg


```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
