---
title: "Nycthemeral effect on the altitudinal flight of Eurasian curlew during his migration"
author: "lorrilliere"
date: "25/08/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

vecPackage=c("ggplot2","ggmap","mapproj","lubridate","maps","mapdata","dplyr","rgdal","maptools","raster","sf","data.table","ggsn","gridExtra","ggrepel","lubridate")
ip <- installed.packages()[,1]

for(p in vecPackage){
     library(p,character.only = TRUE)
}

source("functions/fun_fig_migr_altitude.r")
```


## Adding the statut day, night and crepuscule of all data. 
We did this with the using functions from sun-methods{maptools}. They use algorithms provided by the National Oceanic & Atmospheric Administration (NOAA)



```{r importation daynight computed data, cache=TRUE}
d <- fread("data/Multiselect_20210820_124200_daynight.csv")

```



```{r cars}
head(d)
d <- d[!is.na(day_crepuscule_astro_night),]
dim(d)
```

## Exploration of the day_night variable for the migration flight

We add a season column such that flights from February to April are considered as spring migration flights and flights from June to September are considered as autumn migration flights. 

```{r season}
d[,month := month(UTC_date)]
d[,season := ifelse(month %in% 2:6,"spring",ifelse(month %in% 7:9,"fall",NA)),]
dim(d)

```

Then, we filter the GPS bird locations such as to keep data get when the bird move at lest at 20 km/h and over 50m of altitude and during migration season.

```{r select_flight}
d_flight <- d[speed_km_h > 20 & Altitude_m > 50 & !is.na(season),]
dim(d_flight)
print(head(d_flight))
```



Checking the day night categories. 

```{r hour_day_night}

vecCol <- c("day" = "#d0d1e6","crepuscule_civil"="#74a9cf","crepuscule_astro"="#0570b0","night"="#023858")
d_flight[,day_crepuscule_astro_night := factor(day_crepuscule_astro_night, levels = c("day","crepuscule_civil","crepuscule_astro","night"))]

d_flight[,heure := as.numeric(format(as.POSIXct(UTC_datetime),"%H"))]
d_flight[,year := as.numeric(format(as.POSIXct(UTC_datetime),"%Y"))]

d_flight_agg <- d_flight[,.(ICinf=quantile(heure,.05),median = as.numeric(median(heure)),ICsup=quantile(heure,.975)),by = day_crepuscule_astro_night]
print(d_flight_agg)

gg <- ggplot(data = d_flight[!is.na(heure),], aes(x=heure,fill=day_crepuscule_astro_night)) + geom_histogram(breaks=1:24,colour = NA, alpha= 0.7) + facet_grid(day_crepuscule_astro_night~.,scales="free")
gg <- gg + scale_fill_manual(values=vecCol) + theme(legend.position="none")
print(gg)

```

Checking the solar data in function of day night categories. 

```{r light_day_night}

d_flight_agg <- d_flight[,.(ICinf=quantile(solar_I_mA,.05),median = as.numeric(median(solar_I_mA)),ICsup=quantile(solar_I_mA,.975)),by = day_crepuscule_astro_night]
print(d_flight_agg)

gg <- ggplot(data = d_flight[!is.na(solar_I_mA),], aes(x=solar_I_mA,fill=day_crepuscule_astro_night)) + geom_histogram(colour = NA, alpha= 0.7) + facet_grid(day_crepuscule_astro_night~.,scales="free")
gg <- gg + scale_fill_manual(values=vecCol) + theme(legend.position="none")
print(gg)

```


## the birds

```{r birds}

d_birds <- d_flight[,.(first_datetime= min(UTC_datetime), last_datetime=max(UTC_datetime), 
                duration = round(difftime(max(UTC_datetime),min(UTC_datetime))),
                nb_data_x100 = round(.N /100,2)),by=device_id]
setorder(d_birds, -nb_data_x100)
print(d_birds)

```

In order to keep only birds that seem to be flying normally with the tag, I only keep birds with at least 100 locations in flight.


```{r selected_birds}

the_birds <- d_birds[nb_data_x100 > 1, device_id]

print(the_birds)
```

I keep `r length(the_birds)` birds.

```{r d_flight_birds}
d_flight <- d_flight[device_id %in% the_birds,]
print(dim(d_flight))

```

## altitude of flight 

### For each bird




Here some figures to describe the flight altitudes !

```{r flight_example}

vecCol2 <- vecCol[c(1,4)]

for(i in 1:3){ #length(the_birds)) {

  
  bird_id <- the_birds[i]
  cat("### ",i,"/",length(the_birds)," : ",bird_id,"\n",sep="")
  
  
d_flight_bird <- d_flight[device_id == bird_id,]
  

  
print(summary(d_flight_bird[, Altitude_m]))



gg <- ggplot(data = d_flight_bird, aes(y=direction_deg,x=as.POSIXct(UTC_datetime))) + geom_line() + geom_point(aes(colour=day_night)) 
gg <- gg + facet_grid(season~year, scales="free")
gg <- gg + scale_colour_manual(values=vecCol2) + theme(legend.position="none")
gg <- gg + labs(title = bird_id)
print(gg)

 corner.m <- get_corner(d_flight_bird ,colname_latitude = "Latitude", colname_longitude = "Longitude")
setDF(corner.m)
   xLim=c(corner.m[1,2],corner.m[2,2]);yLim=c(corner.m[2,3],corner.m[1,3])
   
  d_flight_bird_day <- d_flight_bird[day_night == "day",]
 
  # d_flight_bird_day[day_night == "night", day_night := NA]
  
  d_flight_bird_night <- d_flight_bird[day_night == "night",]
 # d_flight_bird_night[day_night == "day", day_night := NA]
  
   
  world1     <- sf::st_as_sf(map('world', plot = FALSE, fill = TRUE))

  gg <- ggplot()+facet_grid(year~season)
    gg <- gg + geom_sf(data = world1,fill="white", colour="#7f7f7f", size=0.5)
    gg <- gg + coord_sf(xlim=xLim,ylim=yLim)
    gg <- gg + geom_point(data=d_flight_bird_night , mapping=aes(x=Longitude,y=Latitude),alpha = 0.8,size=2,colour = vecCol2[2])
        gg <- gg + geom_point(data=d_flight_bird_day , mapping=aes(x=Longitude,y=Latitude),alpha = 0.8,size=2, colour= vecCol2[1])
       gg <- gg + geom_path(data=d_flight_bird , mapping=aes(x=Longitude,y=Latitude,colour=Altitude_m),alpha = 1,size=1)
    gg <- gg + scale_color_gradientn(colours = terrain.colors(10))
  gg <- gg + labs(title = bird_id)
   print(gg) 


gg <- ggplot(data = d_flight_bird, aes(y=Altitude_m,x=as.POSIXct(UTC_datetime))) + geom_line() + geom_point(aes(colour=day_night)) 
gg <- gg + facet_grid(year~season, scales="free")
gg <- gg + scale_colour_manual(values=vecCol2) + theme(legend.position="none")
gg <- gg + labs(title = bird_id)
print(gg)

gg <- ggplot(data = d_flight_bird, aes(y=Altitude_m,x=Latitude)) + geom_line() + geom_point(aes(colour=day_night)) 
gg <- gg + facet_grid(year~season, scales="free")
gg <- gg + scale_colour_manual(values=vecCol2) + theme(legend.position="none")
gg <- gg + labs(title = bird_id)
print(gg)

gg <- ggplot(data = d_flight_bird, aes(y=Altitude_m,x=day_night,fill=day_night)) + geom_boxplot() 
gg <- gg + facet_grid(year~season, scales="free")
gg <- gg + scale_fill_manual(values=vecCol2) + theme(legend.position="none")
gg <- gg + labs(title = bird_id)
print(gg)


}

```



